%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{EXPERIENCE}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Platform: Linux} %
    {8996A Platform AGL/MCTM Projects} %
    {QUALCOMM} % Organization
    {Aug. 2016 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {8996A AGL multimedia architecture design and develop}
        \item {Integrate, maintain and upgrade GStreamer, plugins and dependencies into AGL/MCTM Yocto building system}
        \item {Integrate Qt/Qtmultimedia 5.7.1 into 8996A AGL. Investigate Qtmultimedia QML module and add eglvideonode in it to support hardware accelerations}
        \item {Develop Qt qmlvideo player which supports both software/hardware codecs on 8996A AGL}
        \item {Develop Gtk+ based GStreamer backend and waylandsink media player}
        \item {Develop a GStreamer based application gst-pipeline-builder, which reads JSON configuration files to  construct different multimedia scenarios}
        \item {Investigate Open-AVB and opensource gstreamer AVB plugins. Give proposal to the ethernet AVB module implementation}
        \item {Integrate c2d color converting functions into AGL GStreamer plugins}
        \item {Maintain and upgrade GStreamer/AGL/related kernel drivers, vidc, video in, etc.}
        \item {Early cvbs/ethcam service development: succeed to display cvbs/ethcam input on screen within 2s}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Platform: Linux} %
    {Atlas 7 Serial Chip Solutions} %
    {Cambridge Silicon Radio / QUALCOMM} % Organization
    {Jul. 2014 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Act as project lead of Atlas 7 multimedia part. Design, develop and maintain Atlas 7 Linux Multimedia framework}
        \item {Integrate GStreamer-1.6.1 core, plugins and dependencies to Atlas 7 Linux/Yocto building system}
        \item {New features development and platform specific features development; develop and migrate some proprietary plugins}
        \item {Integrate Qt/Qtmultimedia-5.4.1 into Atlas 7 Linux}
        \item {Develop a cross-platform Qt-Widget based GStreamer backend media player CSRPlayer}
        \item {Develop a Libav based library MediaInfo which is utlized to probe metadata of media files}
        \item {VPP validations for Atlas 7 serial chips. Enable uio driver in Atlas 7 Linux. Migrate VPP random verification tool and verify VPP functions}
        \item {Implement Android Auto / Carplay functions in Atlas 7 Linux and optimize the performance}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Platform: WinCE, Linux, Android} %
    {Prima II \& Atlas VI Serial Chip Solutions} % 
    {Cambridge Silicon Radio} % Organization
    {Apr. 2012 - Dec. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintain multimedia framework on WinCE 6; fix customer issues and support customerized player development}
        \item {Integrate GStreamer and dependencies into Prima II \& Atlas VI Linux and upgrade from 0.10 versions to 1.0 versions}
        \item {Intergrate GStreamer and dependencies into Prima II Android 4.2; implement GStreamer as default media framework to replace libstagefright}
        \item {Develop gstreamer overlay plugin and gstreamer random seek test tool}
        \item {VPP validations for Prima II \& Atlas VI serial chips}
        \item {Support Miracast development on Prima II Android 4.2}
        \item {Vxd391 hardware decoder verifications for Prima II serial chips}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
